Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-10-23 journal/ms.Rmd
journal

Besides these word-level properties, the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words. The lexical structure is best characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words. Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity. These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017].

While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process. In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind. According to this explanation, known as Preferential Attachment (PAT), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99]. In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon. In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment. They called this alternative explanation Preferential Acquisition (PAC).  Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network. These two proposals represent two divergent ideas about the role of lexical networks in acquisition. On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.

```{r growth, fig.cap = "Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
knitr::include_graphics("figs/growth2.png")
```

Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].  The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT. Second, it provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process. Third, it tests the generality of the findings across eight languages.

@@

```{r staticAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect for both production and comprehension. Ranges indicate 95\\% confidence intervals. Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates."}

>>>>

Besides these word-level properties, the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.  The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words (Collins and Loftus, 1975).  Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological similarity. These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @engelthaler2017; @stella2017] add Beckage, 2011 and other people...

While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process. In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind. According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99]. In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon.  In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment. They called this alternative explanation Preferential Acquisition. For clarity of reading, we will rename these scenarios in a ways that reflects how their modes of operation contrast with each other. We will call preferential attachment the Internally-driven mechanism (INT), and preferential acquisition the Externally-driven mechanism (EXT). Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network. These two proposals represent two divergent ideas about the role of lexical networks in acquisition. On the INT proposal, network structure is a causal factor in early word learning; in contrast, on the EXT approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.

```{r growth, fig.cap = "Illustration of the two growth scenarios. Filled circles (I1-I4) represent known words (Internal), and empty circles (E1 and E2) represent words that have not been learned yet (External). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to INT, the node E1 is more likely to enter the lexicon first. For EXT, the utility of a candidate node is its degree in the entire network. According to EXT, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
knitr::include_graphics("figs/growth2.png")
```

@hills2009 found that early networks do not grow through INT as was originally hypothesised by @steyvers2005, but rather through EXT. This finding, though potentially very profound, has only been estabished in the special case of networks that are 1) based on semantic associations, 2) use data from English-learning children, and 3) consider word production as a measure of acqusition. Thus, it could be that the result depends on the domain, culture or/and the measure. In this work, we test the generality of the finding along these three dimesnions.

First, we investigte the mechanism that underlies the growth of phonological networks. Previous studies have analyzed various strcutural properties of adults phonological networks, and found that some of these properties influence the language processes of word recognition and production as well as language-related memory processes (Vitevitch, 2008; Luce & Pisoni, 1998; Chan & Vitevitch, 2009; Chan & Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al. 2018). More relvant to our study is the research that investigates learning in children, and in particualr the finding that words' connectivity in a phonological network is negatively correlated with their age of learning in children (Stokes 2004; Storkel, 2004, 2009). In other words, the finding suggests that words learned earlier tend to sound similar to many other words than a word learned later in life.  This finding is similar to semantics however, does not address the question of the learning mechanism.  In fact, as with semantic networks, the fact that the connectivity in the end-state network predicts AoA can be the outcome of both the internallay- and externally-driven mechanisms (Hills et al. 2009).

Second, we test how the proposed growth mechanims predict word comprehension as compared to production. These two measures differ in their assessment of vocabulary composition (e.g., Benedict, 1979).  Testing both measures is critical as it allows us to investigate the extent to which the mechanism  is infleunced by production constraints (i.e., how difficult a word is to say) as compared to comprehension constraints (i.e., how difficult it is to store or access). If there is consistency across both measures, this would suggest that the growth mechanism captures learning patterns beyond these specific constraints.

Finally, we use developmental data of children in 10 cultures. Such cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechansism is specific to some patterns of learning that emerge due to the particulars of a given language or culture (Bates & MacWhinney, 1987; Slobin, 1985). More precisely, we test whether Hill's finding with English-learning data generalize to other languages, and we test whether this generalization holds for both the semantic and phonological networks, and for both the comprehension and production data.

we test the growth mechanim in the phonological domain. Although previous results showed that ... (Storkel,), the growth mechanim has never been tested. The outcome could enrich the debate as to whether children first learn the words that  (Here I should read the Dautrich paper).   Second, we use developmental data collected from children in 10 cultures. Third, we compare results  using production and comprehension as measures of acuquition.

Why phonological domain is important
Why languages are important
Why comprehension is important

whether phonological networks, like semantic networks, grow by , or if they rather grow by P

Studies that investigate lexical network growth have focused on semantic networks using the English vocabulary and development data based on word production. In particualr,

However, the lexicon is not only strctured semantically

Our work expands this previous research in three ways: 1) we test whether

The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT. Second, it provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process. Third, it tests the generality of the findings across eight languages.

@@

```{r staticAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect. Results are shown for both production and comprehension data. Ranges indicate 95\\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect."}

### 2018-10-23 journal/ms.tex
journal

  \usepackage{graphicx}
  \makeatletter
  \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
  \def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
  \makeatother
  % Scale images if necessary, so that they will not overflow the page
  % margins by default, and it is still possible to overwrite the defaults
  % using explicit options in \includegraphics[width, height, ...]{}
  \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Word Learning as Network Growth: A Cross-linguistic Analysis},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

Besides these word-level properties, the lexical structure (that is, how
words relate to each other) also influences the age of acquisition of
words. The lexical structure is best characterized in terms of a network
where each node represents a word in the vocabulary, and each link
between two nodes represents a relationship between the corresponding
pair of words. Previous studies have investigated early vocabulary
structure by constructing networks using a variety of word-word
relations including shared semantic features, target-cue relationships
in free association norms, co-occurrence in child directed speech, and
phonological similarity. These studies have found that children tend to
produce words that have higher neighborhood density (i.e., high
connectivity in the network) earlier, both at the phonological and the
semantic level (Engelthaler \& Hills, 2017; Hills, Maouene, Riordan, \&
Smith, 2010; Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella,
Beckage, \& Brede, 2017; Storkel, 2009).

While most studies have focused on the static properties of the lexical
network, a few have investigated the underlying developmental process.
In particular, Steyvers and Tenenbaum (2005) suggested that the observed
effects of connectivity are the consequence of how the lexical network
gets constructed in the child's mind. According to this explanation,
known as Preferential Attachment (PAT), highly connected words in the
child's lexicon tend to \enquote{attract} more words over time, in a
rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
what predicts word learning is the \emph{internal} connectivity in the
child's early lexicon. In contrast, Hills et al. (2009) suggested that
what biases the learning is not the connectivity in the child's internal
lexicon but, rather, \emph{external} connectivity in the learning
environment. They called this alternative explanation Preferential
Acquisition (PAC). Figure~\ref{fig:growth} shows an illustration of both
growth scenarios with the same simplified network. These two proposals
represent two divergent ideas about the role of lexical networks in
acquisition. On the PAT proposal, network structure is a causal factor
in early word learning; in contrast, on the PAC approach, network
structure is not internally represented and, therefore, might be an
epiphenomenon of the statistics of the linguistic input.

@@

\caption{Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
\end{figure}

Studies that investigate lexical network growth have focused on semantic
networks using English data (Hills et al., 2010, 2009; Steyvers \&
Tenenbaum, 2005). The novelty of the current study is threefold: First,
it investigates whether phonological networks, like semantic networks,
grow by PAC, or if they rather grow by PAT. Second, it provides a
systematic comparison of both network growth scenarios in the
phonological and the semantic domains and assesses their relative
contribution to the learning process. Third, it tests the generality of
the findings across eight languages.

@@

\includegraphics{ms_files/figure-latex/unnamed-chunk-6-1.pdf}

@@

>>>>

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Word Learning as Network Growth: A Cross-linguistic Analysis},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

Besides these word-level properties, the lexical structure (that is, how
words relate to each other) also influences the age of acquisition of
words. The lexical structure can be characterized in terms of a network
where each node represents a word in the vocabulary, and each link
between two nodes represents a relationship between the corresponding
pair of words (Collins and Loftus, 1975). Previous studies have
investigated early vocabulary structure by constructing networks using a
variety of word-word relations including shared semantic features,
target-cue relationships in free association norms, co-occurrence in
child directed speech, and phonological similarity. These studies have
found that children tend to produce words that have higher neighborhood
density (i.e., high connectivity in the network) earlier, both at the
phonological and the semantic level (Engelthaler \& Hills, 2017; Hills,
Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \&
Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009) add
Beckage, 2011 and other people\ldots{}

While most studies have focused on the static properties of the lexical
network, a few have investigated the underlying developmental process.
In particular, Steyvers and Tenenbaum (2005) suggested that the observed
effects of connectivity are the consequence of how the lexical network
gets constructed in the child's mind. According to this explanation,
known as Preferential Attachment, highly connected words in the child's
lexicon tend to \enquote{attract} more words over time, in a
rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
what predicts word learning is the \emph{internal} connectivity in the
child's early lexicon. In contrast, Hills et al. (2009) suggested that
what biases the learning is not the connectivity in the child's internal
lexicon but, rather, \emph{external} connectivity in the learning
environment. They called this alternative explanation Preferential
Acquisition. For clarity of reading, we will rename these scenarios in a
ways that reflects how their modes of operation contrast with each
other. We will call preferential attachment the Internally-driven
mechanism (INT), and preferential acquisition the Externally-driven
mechanism (EXT). Figure~\ref{fig:growth} shows an illustration of both
growth scenarios with the same simplified network. These two proposals
represent two divergent ideas about the role of lexical networks in
acquisition. On the INT proposal, network structure is a causal factor
in early word learning; in contrast, on the EXT approach, network
structure is not internally represented and, therefore, might be an
epiphenomenon of the statistics of the linguistic input.

@@

\caption{Illustration of the two growth scenarios. Filled circles (I1-I4) represent known words (Internal), and empty circles (E1 and E2) represent words that have not been learned yet (External). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to INT, the node E1 is more likely to enter the lexicon first. For EXT, the utility of a candidate node is its degree in the entire network. According to EXT, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
\end{figure}

Hills et al. (2009) found that early networks do not grow through INT as
was originally hypothesised by Steyvers and Tenenbaum (2005), but rather
through EXT. This finding, though potentially very profound, has only
been estabished in the special case of networks that are 1) based on
semantic associations, 2) use data from English-learning children, and
3) consider word production as a measure of acqusition. Thus, it could
be that the result depends on the domain, culture or/and the measure. In
this work, we test the generality of the finding along these three
dimesnions.

First, we investigte the mechanism that underlies the growth of
phonological networks. Previous studies have analyzed various strcutural
properties of adults phonological networks, and found that some of these
properties influence the language processes of word recognition and
production as well as language-related memory processes (Vitevitch,
2008; Luce \& Pisoni, 1998; Chan \& Vitevitch, 2009; Chan \&
Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al.
2018). More relvant to our study is the research that investigates
learning in children, and in particualr the finding that words'
connectivity in a phonological network is negatively correlated with
their age of learning in children (Stokes 2004; Storkel, 2004, 2009). In
other words, the finding suggests that words learned earlier tend to
sound similar to many other words than a word learned later in life.
This finding however, does not address the question of the learning
mechanism. In fact, as with semantic networks, the fact that the
connectivity in the end-state network predicts AoA can be the outcome of
both the internallay- and externally-driven mechanisms (Hills et al.
2009).

Second, we test how the proposed growth mechanims predict word
comprehension as compared to production. These two measures differ in
their assessment of vocabulary composition (e.g., Benedict, 1979).
Testing both measures is critical as it allows us to investigate the
extent to which the mechanism is infleunced by production constraints
(i.e., how difficult a word is to say) as compared to comprehension
constraints (i.e., how difficult it is to store or access). If there is
consistency across both measures, this would suggest that the growth
mechanism captures learning patterns beyond these specific constraints.

Finally, we use developmental data of children in 10 cultures. Such
cross-linguistic comparison is crucial to test what growth mechanism is
cognitively universal and is used by all children, and what mechansism
is specific to some patterns of learning that emerge due to the
particulars of a given language or culture (Bates \& MacWhinney, 1987;
Slobin, 1985). More precisely, we test whether Hill's finding with
English-learning data generalize to other languages, and we test whether
this generalization holds for both the semantic and phonological
networks, and for both the comprehension and production data.

we test the growth mechanim in the phonological domain. Although
previous results showed that \ldots{} (Storkel,), the growth mechanim
has never been tested. The outcome could enrich the debate as to whether
children first learn the words that (Here I should read the Dautrich
paper). Second, we use developmental data collected from children in 10
cultures. Third, we compare results using production and comprehension
as measures of acuquition.

Why phonological domain is important Why languages are important Why
comprehension is important

whether phonological networks, like semantic networks, grow by , or if
they rather grow by P

Studies that investigate lexical network growth have focused on semantic
networks using the English vocabulary and development data based on word
production. In particualr,

However, the lexicon is not only strctured semantically

Our work expands this previous research in three ways: 1) we test
whether

The novelty of the current study is threefold: First, it investigates
whether phonological networks, like semantic networks, grow by PAC, or
if they rather grow by PAT. Second, it provides a systematic comparison
of both network growth scenarios in the phonological and the semantic
domains and assesses their relative contribution to the learning
process. Third, it tests the generality of the findings across eight
languages.

@@

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{figs/plot_static_preds_all} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAll}
\end{figure}
